---
editor_options: 
  markdown: 
    wrap: 72
---

# Data transformation

To merge all the beer ratings data downloaded by the web scrapper into
single csv file and brewery ratings data downloaded by the web scrapper
into single csv, we used a python script data_merger.py located in the
repository.

To run the data merger and save the merged csv files into data folder
follow below steps.

``` {.bash}
$ cd CraftBeerRatingsAnalysis/brewery_beer_parser

$ python3 data_merger.py
```

\*\* We Added State and Brewery name to beer dataset using the in order
to make it easy for us to join brewery data to beer data in case if we
needed that in our further analysis.

Merged data will be exported to `data` directory in the project.

**Beer data:** `CraftBeerRatingsAnalysis/data/all_beers.csv`

**Brewery Data:** `CraftBeerRatingsAnalysis/data/all_breweries.csv`

```{r}
library(tidyverse)
folder_path <- paste(getwd(), 'data', sep='/')
all_breweries <- read_csv(paste(folder_path, 'all_breweries.csv', sep='/'))
all_beers <- read_csv(paste(folder_path, 'all_beers.csv', sep='/'))
```

## Beer Ratings Data:

**Before Cleaning**

```{r}
rmarkdown::paged_table(sample_n(all_beers, 10))
```

Cleaned up the beer_abv column by removing the characters `% ABV` and
beer_ibu column by removing the characters `IBU` and converted those
columns to a double datatype.

Cleaned up date values to same format and added a new column named year.

Generalized known duplicated beer styles.

Cleaned up state name in cleaned_all_beers to remove `_` 's

```{r}
clean_up_beer_style <- function(beer_style_name) {
  if (beer_style_name == "IPA - Imperial / Double New England / Hazy") {
    return ("Double New England IPA")
  } else if (beer_style_name == "Red Ale - American Amber / Red") {
    return ("Red American Amber")
  } else if (beer_style_name %in% c("IPA - New England / Hazy", "IPA - New England")) {
    return ("New England IPA")
  } else if (beer_style_name == "IPA - Imperial / Double") {
    return ("Double IPA")
  } else if (beer_style_name == "Farmhouse Ale - Saison") {
    return ("Farmhouse Ale")
  } else if (beer_style_name == "Stout - Imperial / Double") {
    return ("Imperial Stout")
  } else if (beer_style_name %in% c("Sour - Fruited Gose",
                                    "Sour - Fruited Berliner Weisse")) {
    return ("Sour - Fruited")
  }
  
  return (beer_style_name)
}

cleaned_all_beers <- all_beers %>%
  mutate(beer_abv = as.double(str_trim(gsub(
    "%\\s+ABV", "", beer_abv
  )))) %>%
  mutate(beer_ibu = as.double(str_trim(gsub(
    "\\s+IBU", "", beer_ibu
  )))) %>%
  mutate(beer_added = as.Date(beer_added, format = "%m/%d/%y")) %>%
  mutate(year = format(beer_added, format = "%Y")) %>%
  mutate(beer_style = sapply(beer_style, clean_up_beer_style))

cleaned_all_beers$state <- gsub('_', ' ', cleaned_all_beers$state)
```

**After Cleaning**

```{r}
rmarkdown::paged_table(sample_n(cleaned_all_beers, 10))
```

## Brewery Ratings Data:

```{r}
rmarkdown::paged_table(sample_n(all_breweries, 10))
```

Removed un-necessary columns in all_breweries data frame and renamed
`name` to `brewery_name` column.

Cleaned breweries with less than 10 beers total and the breweries which
are closed, proprietor, bar as there are mostly useless for our
question.

```{r}
cleaned_all_breweries <-
  all_breweries %>% select(
    name,
    brewery_type,
    city,
    state,
    longitude,
    latitude,
    brewery_id,
    average_rating,
    num_of_ratings,
    num_of_beers,
    total_check_ins,
    unique_user_check_ins,
    brewery
  ) %>% rename(brewery_name = name) %>%
  filter(num_of_beers >= 10) %>% 
  filter(!brewery_type %in% c("proprietor", "bar", "nano", "closed"))
```

**After Cleaning**

```{r}
rmarkdown::paged_table(sample_n(cleaned_all_breweries, 10))
```
